Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-19 edubots_surveys.Rnw
adds descriptive statistical analysis refs #13 refs #24

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)
library(tidyverse)

@@

A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.

@@

>>>>

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)
library(tidyverse)
library(corrplot)

@@

%A few relevant facts from the collected data: teachers with 16-25 years of experience seem more worried about the security of messaging apps and teachers with up to 5 years of experience were more open to adopt messaging apps due to the pandemic; female teachers were more willing to adopt new platforms due to the pandemic, and even to start using safer alternatives; finally, university teachers that did not use them were more reluctant to start using them after the pandemic.

@@

The descriptive analysis in this case is done using a Chi-square test. For the different variables considered, some statistical significance was found for Gender, Sector, and academic Discipline. The values found with the test are: $p-value=0.0034$ for Gender, $p-value=0.0440$ for Sector, and $p-value=0.0180$ for Discipline.
The first column in Fig. \ref{figure:postcovid_chisq} shows the Pearson's residuals of the test for these three variables. Residuals show the difference between the observed and the expected values, with large residuals showing that variables are not truly independent. In this case, blue shows positive contribution and red negative contribution to the test, and saturation shows how large is this contribution in contrast to the expected value by chance. Tables on the right side show adjusted standardized residuals that according to \cite{agresti2013categorical}, if greater than +/-2 for cases with few cells, indicate lack of fit of $H_0$ (bolded in our table). Also, the table shows the percentage of contribution to the test of each cell.

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[c]{0.45\textwidth}
        \centering
<<gender_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54>>=
df <-select(survey.pilot.postCOVID, PostCOVID.changes, Gender, Sector, Experience, Discipline)
df[as.character(df$Gender)!="PNTS", ] -> df1
survey.pilot.postCovidChisq<- droplevels(df1)

covidChanges.vs.Gender<-table(survey.pilot.postCovidChisq$Gender, survey.pilot.postCovidChisq$PostCOVID.changes)
colnames(covidChanges.vs.Gender)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
chisq<-chisq.test(covidChanges.vs.Gender)
corrplot(chisq$residuals, is.corr = FALSE)
    \begin{minipage}[c]{0.45\textwidth}
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|r|r|r|r|}
    \cline{2-5}
                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
    \multicolumn{1}{|l|}{Female} & \textbf{-2.776} & \textbf{2.637} & \textbf{2.028}  & -1.159 \\ 
    \multicolumn{1}{|l|}{} & 14.48\% & \textbf{27.48\%} &  16.46\% & 5.75\% \\ \hline
    \multicolumn{1}{|l|}{Male}   & \textbf{2.776} & \textbf{-2.637} & \textbf{-2.028} & 1.159 \\ 
    \multicolumn{1}{|l|}{} &  8.08\% &  \textbf{15.34\%} & 9.19\% &  3.21\% \\ \hline
    \end{tabular}%
    }
    \begin{minipage}[c]{0.45\textwidth}
<<sector_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
covidChanges.vs.Sector<-table(survey.pilot.postCovidChisq$Sector, survey.pilot.postCovidChisq$PostCOVID.changes)
colnames(covidChanges.vs.Sector)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
chisq<-chisq.test(covidChanges.vs.Sector)
corrplot(chisq$residuals, is.corr = FALSE)
    \begin{minipage}[c]{0.45\textwidth}
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|r|r|r|r|}
    \cline{2-5}
                                 & Did/Do & Didn't/Do & Safer  & Didn' t/Don't \\ \hline
    \multicolumn{1}{|l|}{University} & -1.895 & 0.397 & 0.049  &  \textbf{2.679}\\ 
    \multicolumn{1}{|l|}{University} & 5.81\% & 0.54\% & 0.01\%  &  \textbf{26.48\%}\\ \hline
    \multicolumn{1}{|l|}{Vocational} & -1.895 & -0.397 & -0.049 & \textbf{-2.679}\\ 
    \multicolumn{1}{|l|}{Vocational} & 11.88\% & 1.10\% & 0.02\% & \textbf{54.17\%}\\ \hline
    \end{tabular}%
    }
    \begin{minipage}[c]{0.45\textwidth}
<<discipline_postcovid_chisq, echo=FALSE, fig.width=17/2.54, fig.height=10/2.54, warning=FALSE>>=
survey.pilot.postCovidChisq %>%mutate(Discipline = ifelse(as.character(Discipline) == "No", "Hum/Social Sciences", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Other", "Hum/Social Sciences", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Engineering", "Tech/Engineering", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Technology", "Tech/Engineering", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Humanities", "Hum/Social Sciences", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Social Sciences", "Hum/Social Sciences", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Sciences", "Biomed/Sciences", as.character(Discipline))) %>%
  mutate(Discipline = ifelse(as.character(Discipline) == "Biomedicine", "Biomed/Sciences", as.character(Discipline)))->survey.pilot.postCovidChisq
covidChanges.vs.Discipline<-table(survey.pilot.postCovidChisq$Discipline, survey.pilot.postCovidChisq$PostCOVID.changes)
colnames(covidChanges.vs.Discipline)<- c("Did/do", "Didn't/do","safer", "Didn't/don't")
chisq<-chisq.test(covidChanges.vs.Discipline)
corrplot(chisq$residuals, is.corr = FALSE)
    \begin{minipage}[c]{0.45\textwidth}
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|r|r|r|r|}
    \cline{2-5}
                                 & Did/Do & Didn't/Do & Safer & Didn' t/Don't \\ \hline
    \multicolumn{1}{|l|}{Biomed/Sciences} & -1.202 &  0.715 & 1.424 & -0.635 \\ 
    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.12\% &  2.32\% & 9.34\% & 1.99\% \\ \hline
    \multicolumn{1}{|l|}{Hum/Social} &  \textbf{-2.869} & \textbf{2.069} &  1.592 & 0.274\\ 
    \multicolumn{1}{|l|}{Hum/Social} &  16.58\% & \textbf{18.13\%} &  10.88\% & 0.35\%\\ \hline
    \multicolumn{1}{|l|}{Tech/Engineering} &  \textbf{3.382} &  \textbf{-2.322} &  \textbf{-2.461} & 0.254\\ 
    \multicolumn{1}{|l|}{Tech/Engineering} &  11.92\% &  11.80\% &  \textbf{13.43\%} & 0.15\%\\ \hline
    \end{tabular}%
    }
    \caption{.}
\label{figure:postcovid_chisq}
